### 2015-10-18 Assignment I/Assignment1-Ditz_Schroeder-WS15-16.tex
kleine veränderung am tex file

  \section*{Exercise 1 - \textsl{Smith Waterman today}}
	  The 30 years old Smith-Waterman (SW) algorithm is one of the fundamental algorithms in bioinformatics. This algorithm allows in a biological sense for example the detection of Domains in a protein or a Protein in a larger sequence. But the dynamic programmed algorithm has to face the problem of complexity of $O(n\times m)$. This complexity is getting a problem when starting to compare large sequences or even whole genomes.
	  The classical example for todays usage of the Smith Waterman algorithm is the BLAST algorithm. \cite{blast}

@@

  \section*{Exercise 3 - \textsl{Programming assignment: Needleman-Wunsch alignment}}
  One task was to handle command line options. We wrote a new class to have a modular 
  and easy way to provide this functionality. The java package \textit{args4j} has everything
  we need. So we used that package to write our own option handler class. The code can 
  be found in \textit{CommandLineParser.java}. We did the same with gap penalties. A
  gap penalty class gives one the advantage of modular gap handling. If a gap penalties are
  needed, just reuse this class.\\
  A new member function of our NeedlemanWunsch class takes care of file writing. If a user 
  wants the resulting alignment in a FastA file, this function takes care of it.

\begin{thebibliography}{widestlabel}
	\bibitem[Li, H., Homer, N.]{blast} 	
	Li, H., Homer, N. (2010). A survey of sequence alignment algorithms for next-generation sequencing. Briefings in Bioinformatics, 11(5), 473–483. http://doi.org/10.1093/bib/bbq015
\end{thebibliography}

>>>>

  \section*{Exercise 1 - \textsl{}}

@@

  \section*{Exercise 3 - \textsl{Programming assignment: Needleman-Wunsch alignment}}
  One task was to handle command line options. We wrote a new class to have a modular 
  and easy way to provide this functionality. The java package \textit{args4j} has everything
  we need. So we used that package to write our own option handler class. The code can 
  be found in \textit{CommandLineParser.java}. We did the same with gap penalties. A
  gap penalty class gives one the advantage of modular gap handling. If a gap penalties are
  needed, just reuse this class.\\
  A new member function of our NeedlemanWunsch class takes care of file writing. If a user 
  wants the resulting alignment in a FastA file, this function takes care of it. To fullfil 
  that task it uses a BufferedWriter and FileWriter.
